Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-11 docs/ms.tex
Update ms.tex
update mx.tex

\caption{The figure shows the estimated $g_{1}$ values minus the true (input)
$g_{1}^{true}$. The distribution range of $g_{1}^{true}$ is from
-0.1 to 0.1. Originally there are 640,000 true $g_{1}$. We bin the
plot for presentation purpose. The data point and error bars are the weighted
 average and  variance of $\delta g_{1}$ in each bin. The blue
line is the result of weighted linear fit of the original 640,000 data points
with sample standard deviation as error bar.}
\end{figure}

@@

\caption{\protect\includegraphics{averagebias}\protect\includegraphics{bayesianbias}}

The upper panel shows the systematic bias of the mean ellipticity
estimator. m=$7.9\times10^{-4}\pm0.0029$ , c=$3.63\times10^{-4}\pm1.637\times10^{-4}$.The
lowwer panel shows the systembatic bias of the sample mean. m=$-0.06\pm0.00253$,
c=$3\times10^{-4}\pm1.55\times10^{-4}$ . For both cases the m,c values
are obtained from unweighted linear fit using 640,000 data points. We bin the plot into ten bins for presentation
purpose. The black square denotes the mean of $\Delta g$ in that
bin.
\end{figure}

>>>>

\caption{The figure shows the estimated $g_{1}$ values minus the true (input)
$g_{1}^{true}$. The distribution range of $g_{1}^{true}$ is from
-0.1 to 0.1. Originally there are 640,000 true $g_{1}$. We bin the
plot for presentation purpose. The data point and error bars are the weighted
 average and  variance of $\delta g_{1}$ in each bin. The blue
line is the result of weighted linear fit of the original 640,000 data points
with sample standard deviation as error bar.}
\end{figure}
Suppose we have perfect measurements on galaxy shape, the measures
ellipticity is equall to the true lensed ellipticity. The mean ellipticity
estimator has following expression :
\begin{equation}
<\epsilon_{\ell}>=g^{t}+<\epsilon_{0}>+<(\epsilon_{0}+g^{t})[-g^{t*}\epsilon_{0}+O(g^{t*}\epsilon_{0})]>
\end{equation}
When the unlensd ellipticity is purely isotropic ,we have $<\epsilon_{\ell}>=g^{t}$ . In this case, the mean ellipticity estimator is 
unbiased.
Meanwhile we find that simply using the posterior mean as the estimator of g will lead to a significant bias. 
Figure 3 shows the result of bias test for both mean ellipticity and posterior mean estimator.

@@

\includegraphics[scale=0.48]{fig/averagebias}

\includegraphics[scale=0.48]{fig/bayesianbias}

\caption{The upper panel shows the systematic bias of the mean ellipticity
estimator. m=$7.9\times10^{-4}\pm0.0029$ , c=$3.63\times10^{-4}\pm1.637\times10^{-4}$.The
lowwer panel shows the systembatic bias of the sample mean. m=$-0.06\pm0.00253$,
c=$3\times10^{-4}\pm1.55\times10^{-4}$ . For both cases the m,c values
are obtained from unweighted linear fit using 640,000 data points. We bin the plot into ten bins for presentation
purpose. The black square denotes the mean of $\Delta g$ in that
bin.}
\end{figure}
